---
title: "Data_Analysis_Project1"
author: "Parker Hicks"
date: "3/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(dplyr)
library("car")
NCA <- Bugando_NCA
```

###Graph
```{r}
ggplot(NCA, aes(x = Sex, y = HC)) +
  geom_boxplot() +
  theme_minimal() +
  theme(text = element_text(size=20)) +
  ggtitle("Head Circumference of Males and Females from the Ngorongoro Conservation Area") + 
  xlab("Sex (Female/Male)") +
  ylab("Head Circumference (cm)")
```

### Hypothesis
Null: The head circumferences of males and females from the Ngorongoro Conservation Area are not statistically different.

Alternative: The head circumferences of males and females from the Ngorongoro Conservation Area are statistically different.

### Summary Statistics
## Mean
```{r}
mean_HC <- mean(NCA$HC)
cat("The mean head circumference among males and females was", mean_HC, "cm.")
```

```{r}
#Group means were taken from the t-test below
mean_HC_males <- 31.96943
mean_HC_females <- 31.94454
cat("The mean head circumference of males was", mean_HC_males, "cm.")
cat(" The mean head circumference of females was", mean_HC_females, "cm.")
```

##Confidence Intervals
```{r}
male_data <- subset(Bugando_NCA, Sex=="M", select=HC)
female_data <- subset(Bugando_NCA, Sex=="F", select=HC)

male_confint <- t.test(male_data)$conf.int
female_confint <- t.test(female_data)$conf.int

male_confint
female_confint

NCA_confint <- t.test(NCA$HC)$conf.int
NCA_confint
```

## Standard error
```{r}
ser <- function(x){
  st_dev <- sd(x)
  n <- length(x)
  st_er <- st_dev / sqrt(n)
  
  return(st_er)
}

st_er_males <- ser(male_data$HC)
st_er_females <- ser(female_data$HC)
st_er_overall <- ser(NCA$HC)

st_er_males
st_er_females
st_er_overall
```

### Statistical Tests
## Equal variance test
```{r}
var.test(HC ~ Sex, data=NCA, alternative="two.sided")
```
The variances of the data are not statistically different from one another (F=1.28, p>0.05, two-sided F-test).

## Shapiro-Wilk test for normallity
```{r}
shapiro.test(NCA$HC)
```
The data are not significantly different than a normal distribution (W=0.988, p>0.05, Shapiro-Wilk test).

## Two-sided t-test
```{r}
t.test(data=NCA, HC ~ Sex, alternative="two.sided", var.equal=FALSE)
```
The head circumferences of males and females from the Ngorongoro Conservation Area are not statistically different from one another (t[113.67]=-0.084, p>0.05, two-sided t-test).









