---
title: "Data_Analysis_Project2"
author: "Parker Hicks"
date: "4/21/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

if(!require(car)) install.packages("car")
if(!require(ggplot2)) install.packages("ggplot2")
if(!require(ggpubr)) install.packages("ggpubr")
if(!require(FSA)) install.packages("FSA")
if(!require(dplyr)) install.packages("dplyr")
if(!require(binom)) install.packages("binom")
if(!require(rcompanion)) install.packages("rcompanion")
if(!require(multcomp)) install.packages("multcomp")

library(readr)
library(ggplot2)
library(binom)
library(dplyr)
library(FSA)
library(car)
library(rcompanion)
library(multcomp)
library(ggpubr)
```

# Data
```{r}
tit_data <- read.csv(("/Users/parkerhicks/Desktop/Biostats_data/tit_fitness_data.csv"), stringsAsFactors = TRUE)

tit_dataOmit <- na.omit(tit_data)
```

# Hypothesis

Null: 
There is no difference in the brood size of wild great tits on the basis of weight.
There is no difference in the brood size of wild great tits on the basis of wing size.
There is no difference in the brood size of wild great tits on the basis of weight and wing size

Alternative:
There is a difference in the brood size of wild great tits on the basis of weight.
There is a difference in the brood size of wild great tits on the basis of wing size.
There is a difference in the brood size of wild great tits on the basis of weight and wing size

#Graph






