---
title: "Lab_ANOVA"
author: "Parker Hicks"
date: "4/7/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(binom)
library(dplyr)
library(FSA)
library(car)
library(rcompanion)
library(multcomp)
```

## Data
```{r}
stress_echo_data <- read.csv(("Desktop/W11_Lab_stressEcho_DATA.csv"), stringsAsFactors = TRUE)
hr_smoke_data <- subset(stress_echo_data, select=c("bhr", "hxofCig"))
hr_smoke_omit <- na.omit(hr_smoke_data)
```

## Graph
```{r}
ggplot(hr_smoke_omit, aes(x=hxofCig, y=bhr)) +
  geom_violin() +
  stat_summary(fun=mean, geom="point", size=3, color="blue") +
  stat_summary(fun.data = mean_se, geom="errorbar", width=0.33, color="blue") +
  theme_minimal()
```

## Descriptive Statistics
```{r}
Summarize(bhr ~ hxofCig, hr_smoke_omit)
```

## Test Statistics
H0: There is no significant difference of base heart rate between individuals who are heavy or moderate smokers or non-smokers.

Ha: There is at least one significant difference of base heart rate between individuals who are heavy or moderate smokers or non-smokers.

### One-way ANOVA
```{r}
bhr_lm <- lm(bhr ~ hxofCig, hr_smoke_omit)
anova(bhr_lm)
```

## Assumption tests
```{r}
qqnorm(bhr_lm$residuals)
qqline(bhr_lm$residuals)

# Shapiro-Wilk test of residuals
shapiro.test(bhr_lm$residuals)
```

## Levene's Test
```{r}
leveneTest(bhr ~ hxofCig, hr_smoke_omit)
```

```{r}
plot(bhr_lm)
```

## Inferential Statistics
### Confidence Intervals
```{r}
confint(bhr_lm)
```

### Standard Error
```{r}
sem <- function(x){
  st_dev <- sd(x)
  st_er <- (sqrt(st_dev)) / length(x)
}

summarize(hr_smoke_omit, Standard_Error = sem(bhr))
```

## R-Squared
```{r}
summary(bhr_lm)$r.squared
```

## INTERPRETATION

There was no significant relationship between the basal heart rates of heavy, moderate, and non-smokers (ANOVA, F(2,555)= 2.5322; p=0.0804). The extent of smoking only explained 0.09% of the basal heart rates of the subjects (R=0.00904). Post hoc comparisons were not performed because the ANOVA test resulted in a non-significant p-value. The data did not meet the assumption of normality most likely due to extreme outliers, but they did meet the assumption of equal variance. Alternative tests were not performed because a majority of the data aligned with the qqline (Figure 1) except for a some outliers and the data met homogeneity of variance. The mean(± SE) of the basal heart rates of heavy, moderate, and non-smokers were 77.803(± 0.0359), 73.565(± 0.0263), and 75.060(± 0.0127) respectively (Figure 2). We failed to reject the null hypothesis, but further tests should be performed to identify any differences in other randomly sampled groups. 

### Figure 1
```{r}
qqnorm(bhr_lm$residuals)
qqline(bhr_lm$residuals)
```
QQ plot of the linear model from basal heart rate as a function of the extent of smoking.

### Figure 2
```{r}
ggplot(hr_smoke_omit, aes(x=hxofCig, y=bhr)) +
  geom_violin() +
  stat_summary(fun=mean, geom="point", size=3, color="blue") +
  stat_summary(fun.data = mean_se, geom="errorbar", width=0.33, color="blue") +
  theme_minimal() +
  ggtitle("Basal Heart Rate as a Function of Smoking Habits") +
  xlab("Extent of Smoking") +
  ylab("Basal Heart Rate (bpm)")
```
A violin plot displaying the basal heart rates (bpm) as a function of the subjects' smoking habits.

